---
title: "Result plots"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list=ls(all=TRUE))
library(MASS)
library(foreach)
library(RBesT)
library(ggpubr)
library(TeachingDemos)
library(PSweight)
library(ggplot2)
library(foreach)
library(psrwe)
library(survival)
library(reshape2)
```

The simulation is done through 4 methods:

+ Method A: Compare internal treatment vs. internal control using regression (response ~ trt)
+ Method B: Simply combine internal control with external control and use regression (response ~ trt)
+ Method C: IPW weighting on external data
+ Method D: Our method, IPW weighting + MEM


### With no unobserved confounders

The simulation is done through 9 scenarios:

+ Scenario 1: 
\
assume internal data (treatment arm) arise from the same population as external

+ Scenario 2-3: 
\
there is 1 observed confounder with strong negative effect on the outcome, i.e. Pr(liver_met=1) = 0.2 or 0.8 for internal

+ Scenario 4-5: with observed confounders
\
there is 1 observed confounder with strong postive effect on the outcome, i.e. Pr(ras=1)= 0.2 or 0.8 for internal

+ Scenario 6-7: with unobserved confounders
\
there are 1 observed confounder with medium negative effect on the outcome, i.e. Pr(=1) = 0.2 or 0.8 for internal

+ Scenario 8-9: with unobserved confounders
\
there are 1 observed confounder with medium positive effect on the outcome, i.e. Pr(=1) = 0.2 or 0.8 for internal


### With unobserved confounders

The simulation is done through 9 scenarios:

+ Scenario 1: 
\
assume internal data (treatment arm) arise from the same population as external

+ Scenario 2-3: 
\
there is 1 unobserved confounder with strong negative effect on the outcome, i.e. Pr(liver_met=1) = 0.2 or 0.8 for internal

+ Scenario 4-5: 
\
there is 1 unobserved confounder with strong postive effect on the outcome, i.e. Pr(ras=1)= 0.2 or 0.8 for internal

+ Scenario 6-7: 
\
there are 1 unobserved confounder with medium negative effect on the outcome, i.e. Pr(=1) = 0.2 or 0.8 for internal

+ Scenario 8-9:
\
there are 1 unobserved confounder with medium positive effect on the outcome, i.e. Pr(=1) = 0.2 or 0.8 for internal

```{r,echo=F, fig.width=60, fig.height=60}
S <- 9
df <- readRDS(paste0("/Users/oliviazhang/Desktop/MEM/result/sim_surv_NULL.RData"))
df2 <- readRDS(paste0("/Users/oliviazhang/Desktop/MEM/result/sim_surv_ALT.RData"))
Rejection <- rbind(df$power,df2$power)

Rejection <- melt(Rejection, id.vars = c(paste("Scenario-", 1:S, sep="")))
Rejection$True_beta <- rep(c(rep("Null",4),
                         rep("Alternative",4)),S)
names(Rejection) <- c("Method","Scenario","value","True_beta")

scenario_des <- as_labeller(c(
  'Scenario-1'="Scenario 1: RCT",
  'Scenario-2'="Scenario 2: strong negative confounder, P(=1)=0.8",
  'Scenario-3'="Scenario 3: strong negative confounder, P(=1)=0.2",
  'Scenario-4'="Scenario 4: strong postive confounder, P(=1)=0.2",
  'Scenario-5'="Scenario 5: strong postive confounder, P(=1)=0.8",
  'Scenario-6'="Scenario 6: medium negative confounder, P(=1)=0.2",
  'Scenario-7'="Scenario 7: medium negative confounder, P(=1)=0.8",
  'Scenario-8'="Scenario 8: medium postive confounder, P(=1)=0.2",
  'Scenario-9'="Scenario 9: medium postive confounder, P(=1)=0.8"
))

print(ggplot(Rejection, aes(x=factor(True_beta,
                               levels = c("Null","Alternative")), y=value, fill = Method)) +
  geom_bar(stat="identity", position=position_dodge())+
  facet_wrap(~Scenario, labeller = scenario_des, nrow =3) +
  theme(legend.title = element_text(colour="black", size=40, face="bold"),
        legend.text = element_text(size=60),
        legend.key.size = unit(2, 'cm'),
        legend.key.height = unit(2, 'cm'), 
        legend.key.width = unit(2, 'cm'),
        legend.position="bottom",
        plot.title = element_text(size=100),
        strip.text = element_text(size = 60))+
  labs(title="Type I error and Power with NO unobserved confounders",
       fill = "")+
  xlab("")+
  ylab("")+
  scale_fill_discrete(labels = c("Internal only", "IPW", "MEM+IPW", "Pull all external"))+
  geom_text(aes(label=value), position = position_dodge(0.9), size=20))
```

```{r, echo=F, fig.width=60, fig.height=60}
df <- readRDS(paste0("/Users/oliviazhang/Desktop/MEM/result/sim_surv_unobs_NULL.RData"))
df2 <- readRDS(paste0("/Users/oliviazhang/Desktop/MEM/result/sim_surv_unobs_ALT.RData"))
Rejection <- rbind(df$power,df2$power)

Rejection <- melt(Rejection, id.vars = c(paste("Scenario-", 1:S, sep="")))
Rejection$True_beta <- rep(c(rep("Null",4),
                         rep("Alternative",4)),S)
names(Rejection) <- c("Method","Scenario","value","True_beta")


print(ggplot(Rejection, aes(x=factor(True_beta,
                               levels = c("Null","Alternative")), y=value, fill = Method)) +
  geom_bar(stat="identity", position=position_dodge())+
  facet_wrap(~Scenario, labeller = scenario_des, nrow =3) +
  theme(legend.title = element_text(colour="black", size=40, face="bold"),
        legend.text = element_text(size=60),
        legend.key.size = unit(2, 'cm'),
        legend.key.height = unit(2, 'cm'), 
        legend.key.width = unit(2, 'cm'),
        legend.position="bottom",
        plot.title = element_text(size=100),
        strip.text = element_text(size = 60))+
  labs(title="Type I error and Power with unobserved confounders",
       fill = "")+
  xlab("")+
  ylab("")+
  scale_fill_discrete(labels = c("Internal only", "IPW", "MEM+IPW", "Pull all external"))+
  geom_text(aes(label=value), position = position_dodge(0.9), size=20))
```